Covid-19 Fields Survey Data Protocol

### 2023-01-15 protocol/Background_and_methods_Jan_12.qmd
Working to fix figure

library(weights)
library(here)
library(survey)
library(magrittr)
library(tidyverse)
library(lme4)
library(kableExtra)
library(modelsummary)
library(gtsummary)

@@

```{r, model-table}
#| label: tbl-model
#| tbl-cap: "Logistic Regression Model Estimates"
#| message: false
#| echo: false
#| warning: false

# models<-list(model1,model2,model3)
# # 
# modelsummary(models,exponentiate = TRUE, stars = T, statistic = c("conf.int",
#                           "p = {p.value}"))
# 
#  
# modelsummary(model1,exponentiate = TRUE, stars = T, statistic = c("conf.int",
#                           coef_omit = c(1),
#                           "p = {p.value}"))

# model_tbl1<-model1 %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_labels()%>%
#   modify_header(label = "**Variable**")
# # 
# # test<-summary(model1)
# # 
# model_tbl1<-model1 %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   select(variable, estimate, p.value) %>%
#   filter(p.value <= 0.05)%>%
#   kbl()%>%
#   as_kable_extra() %>%
#   kableExtra::kable_styling(
#     font_size = 8
#   )
# 
# # 
# model_tbl2<-model2 %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_labels()%>%
#   modify_header(label = "**Variable**")%>%
#   as_kable_extra() %>%
#   kableExtra::kable_styling(
#     font_size = 8
#   )
# 
# model_tbl3<-model3 %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_labels()%>%
#   modify_header(label = "**Variable**")%>%
#   as_kable_extra() %>%
#   kableExtra::kable_styling(
#     font_size = 10
#   )

# model_tbl3
# 
# model_tbl3
# 
# tbl_merge_model<-
#   tbl_merge(
#     tbls = list(model_tbl1,model_tbl2,model_tbl3),
#     tab_spanner = c("**Model 1**","**Model 2**", "**Model 3**")
#   )%>%
#   as_flex_table()
# 
# tbl_merge_model
#

# modelsummary(model3,exponentiate = TRUE, stars = T, statistic = c("conf.int",
#                           "p = {p.value}"))

>>>>

library(weights)
library(here)
library(survey)
library(magrittr)
library(tidyverse)
library(lme4)
library(kableExtra)
library(modelsummary)
library(gtsummary)
library(patchwork)

@@

```{r, model-table}
#| message: false
#| echo: false
#| warning: false
#| fig-width: 8
#| fig-height: 8

 # models<-list("First Model"=model1,
 #              "Second Model"=model2,
 #              "Third Model"=model3)

a<-modelplot(model1,coef_omit = ':')+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")

b<-modelplot(model2,coef_omit = ':')+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("Second Model")

c<-modelplot(model3,coef_omit = ':')+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("Third Model")

a+b+c+plot_layout(guides = 'collect')+plot_annotation(title="Fixed effects of all models")& theme(legend.position = 'bottom')

d<-modelplot(model1,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")

e<-modelplot(model2,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")

f<-modelplot(model3,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")

d+e+f+plot_layout(guides = 'collect')+plot_annotation(title="Interaction effects of all models") & theme(legend.position = 'bottom')

#  modelsummary(models,exponentiate = TRUE, stars = T, statistic = c("conf.int",
#                            "p = {p.value}"))
# 
# 
#  modelsummary(model1,exponentiate = TRUE, stars = T, statistic ="conf.int")
# 
#  model_tbl1<-model1 %>%
#    tbl_regression(exponentiate = TRUE) %>%
#    bold_labels()%>%
#    modify_header(label = "**Variable**")
# 
#   test<-summary(model1)
# 
#  model_tbl1<-model1 %>%
#    tbl_regression(exponentiate = TRUE) %>%
#    select(variable, estimate, p.value) %>%
#    filter(p.value <= 0.05)%>%
#    kbl()%>%
#    as_kable_extra() %>%
#    kableExtra::kable_styling(
#      font_size = 8
#    )
# 
# 
# 
# # # 
# # model_tbl2<-model2 %>%
# #   tbl_regression(exponentiate = TRUE) %>%
# #   bold_labels()%>%
# #   modify_header(label = "**Variable**")%>%
# #   as_kable_extra() %>%
# #   kableExtra::kable_styling(
# #     font_size = 8
# #   )
# # 
# model_tbl3<-model3 %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_labels()%>%
#   modify_header(label = "**Variable**")%>%
#   as_kable_extra() %>%
#   kableExtra::kable_styling(
#     font_size = 10
#   )
# 
# # model_tbl3
# # 
# # model_tbl3
# # 
# # tbl_merge_model<-
# #   tbl_merge(
# #     tbls = list(model_tbl1,model_tbl2,model_tbl3),
# #     tab_spanner = c("**Model 1**","**Model 2**", "**Model 3**")
# #   )%>%
# #   as_flex_table()
# # 
# # tbl_merge_model
# # 
# 
#  modelsummary(model3,exponentiate = TRUE, 
#               stars = T, 
#               estimate = "{estimate} [{conf.low}, {conf.high}]",
#               #statistic = NULL
#               )

### 2023-01-15 protocol/Background_and_methods_Jan_12.tex
Working to fix figure

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/13/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, boxrule=0pt, enhanced, breakable, interior hidden]}{\end{tcolorbox}}\fi

@@

\begin{table}

>>>>

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/15/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, breakable, sharp corners, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

\includegraphics{Background_and_methods_Jan_12_files/figure-pdf/model-table-1.png}

\includegraphics{Background_and_methods_Jan_12_files/figure-pdf/model-table-2.png}
